% Minutes for 4/7 in class meeting
\documentclass{article}

\title{Minutes from Apr 7}
\author{Matt Edwards}
\date{7th April 2014}

\usepackage{fullpage}
\usepackage{hyperref}

\begin{document}

\maketitle

\begin{description}
\item[Location:] In Class
\item[Present:] Wanli, Matt
\item[Absent:] Adam
\end{description}

\section{Role assignment}
\begin{description}
\item[Matt:]Recorder \& Checker
\item[Wanli:]Coordinator
\item[Adam:]Monitor - Update (4/8 wz): Since Adam has dropped the class, Wanli will also act as Monitor
\end{description}

\section{Tasks}
\begin{enumerate}
\item Group Contract, Due Weds Apr 9 (hardcopy)
\item At least 3 questions, Due Weds Apr 9 (discussion, no turn in)
\item Create Git Repository and add users
\end{enumerate}

\subsection{Group Contract Ideas}
Matt \& Wanli suggested items to include on the group contract. No finalization decisions were made.

\begin{itemize}
\item ``We commit to a timely response to e-mail discussions, < 24 hours."
\item ``I will commit to timely progress on individual tasks, and will inform the group if that is not possible, or difficulty arises."
\item ``I will show up to meetings on time, and will contact the group if that is not possible."
\item ``I will make every effort to give sufficient warning of an absence so that rescheduling is possible."
\item ``I will speak up if I do not understand a task."
\end{itemize}

\subsection{Question Ideas}
\subsubsection{References}
\begin{itemize}
\item Page with Link to PDF Of Survey: \url{http://www.census.gov/acs/www/about_the_survey/forms_and_instructions/}
\item PUMS Documentation: \url{http://www.census.gov/acs/www/data_documentation/public_use_microdata_sample/}
\end{itemize}

\subsubsection{Question Topics}
(!) means someone expressed interest in pursuing this. Matt \& Wanli went through the survey, tossed out ideas and discussed some. These are the topics tossed out:

\begin{itemize}
\item Education related to ...???
\item Language spoken
\item Change of residence type
\item Insurance: Change due to Obamacare is probably out of the question, but could look at number of enrolled vs not.
\item Difficulty in hearing or speaking
\item Marital status/Birth
\item Army Service(!)\\
  as related to education level or insurance\\
  Matt suggested to see how education level and/or income related for those who had never served vs those who had served, but were now retired.
\item Transportation to Work (!)
  by state? by sex? by age? by county? 
\item Commute time
\item Actively job hunting
\item Types of employment
\item Total income last 12 months (see above under Army Service)
\item Income \& Education (kind of a gimme question, we would expect income to be higher with more education.)
\item - Update (4/8 wz): What's the favorite type of fuel for heating of an RV owner/mobile home owner/family house owner? (!)
\item - Update (4/8 mhe) what is the cost/per person ratio between owning and renting a home? has that gap widened since X years ago? (assuming same questions asked then) (!)
\end{itemize}


\section{Git Busy}
Wanli created the Git repository and added Matt as a user.
Unable to add Adam, as we do not have his information.
Update (4/8 wz): Adam has dropped the course, so Matt and Wanli will work on this project by themselves.

\section{To Do:}
\subsection{Finalize group contract: Everyone}
\begin{itemize}
\item Everyone: Update and/or approve teh list of commitments by 8 pm on Tuesday, April 8th.
\item Matt: Compile document, print and bring to class Weds for sign \& turn in.
\item DONE - 4/8
\end{itemize}

\subsection{Questions: Everyone}
\begin{itemize}
\item Everyone: Refine existing question topics or suggest new ones. Each individual in group should have at least one unique question of interest ready to discuss on Weds. Inform group of which questions you'd like to take "charge" of.
\item DONE - 4/8
\end{itemize}

\subsection{Post meeting minutes: Matt}
\begin{itemize}
\item Type up and post minutes.
\item DONE - 4/7.
\end{itemize}

\subsection{4/8 Update}
\begin{itemize}
  \item Copied changes from .txt file that Wanli made due to Adam Leaving
  \item Completed: Group contract: printed, ready to sign in Am. .tex file added to repository.
  \item Completed: two questions each
\end{itemize}




\end{document}